\LARGE \bf Planning with Attitude

### 2020-10-12 paper/main.tex
Add some more discussion on flexsat

\section{Experiments} \label{sec:experiments}
    In this section we present several trajectory optimization problems for systems that
    undergo large changes in attitude: an airplane barrel roll, a quadrotor flip, and a
    satellite with flexible solar panels that must slew to a new orientation while avoiding a 
    keep-out zone. All results were run on a desktop computer with an 
    AMD Ryzen 2950x processor with 40 GB of RAM. 
    All problems are run using ALTRO, first without any of the modifications presented 
    in the current paper, analagous to the naive Newton's method in section \ref{sec:Wahbas} and labeled ``naive'', and then using the modifications listed
    in Sec. \ref{sec:trajopt} and the geodesic cost function described in Sec. \ref{sec:geodesic},
    labeled ``modified''.
    Timing results are summarized in Table \ref{tab:timing_results}.
    All experiments were solved to a constraint satisfaction tolerance of $10^{-5}$ and 
    discretized with a 4th order Runge-Kutta integrator.
    Code for all experiments is available on 
    \href{https://github.com/RoboticExplorationLab/PlanningWithAttitude}
    {GitHub\footnote{\url{https://github.com/RoboticExplorationLab/PlanningWithAttitude}}}.

@@

@@

        \begin{figure}[h]
            \centering
            \includegraphics[width=\columnwidth]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by iterative MLQR using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

        \begin{figure}[h]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint convergence when solving the barrel roll problem. Compares 
            the convergence of the original version of ALTRO versus the new, modified version
            that optimizing on the error state.}
            \label{fig:c_max_convergence}
        \end{figure}

>>>>

\section{Experiments} \label{sec:experiments}
    In this section we present several trajectory optimization problems for systems that
    undergo large changes in attitude: an airplane barrel roll, a quadrotor flip, and a
    satellite with flexible solar panels that must slew to a new orientation while
    avoiding a keep-out zone. All results were run on a desktop computer with an AMD
    Ryzen 2950x processor with 40 GB of RAM. All problems are run using ALTRO, first
    without any of the modifications presented in the current paper, analagous to the
    naive Newton's method in section \ref{sec:Wahbas} and labeled ``naive'', and then
    using the modifications listed in Sec. \ref{sec:trajopt} and the geodesic cost
    function described in Sec. \ref{sec:cost_functions}, labeled ``modified''. Timing
    results are summarized in Table \ref{tab:timing_results}. All experiments were solved
    to a constraint satisfaction tolerance of $10^{-5}$ and discretized with a 4th order
    Runge-Kutta integrator. Code for all experiments is available on
    \href{https://github.com/RoboticExplorationLab/PlanningWithAttitude}
    {GitHub\footnote{\url{https://github.com/RoboticExplorationLab/PlanningWithAttitude}}}.

@@

        The modifications didn't have a significant impact on runtime performance for this
        example. In our experience, the computational benefits of the proposed methodology are
        problem-dependent, especially for highly nonlinear systems. The following examples result
        in more dynamic and aerobatic behaviors, where the computational benefit of the proposed
        methodology is significant, including an example where the naive method failed to find a
        good solution.

@@

        \begin{figure}[ht]
            \centering
            \includegraphics[width=\columnwidth]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by iterative MLQR using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

        \begin{figure}[ht]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint convergence when solving the barrel roll problem. Compares 
            the convergence of the original version of ALTRO versus the new, modified version
            that optimizing on the error state.}
            \label{fig:c_max_convergence}
        \end{figure}
